---
title: "EarthqVis"
author: "Mot Hakimi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_width: 12
fig_height: 4 
vignette: >
  %\VignetteIndexEntry{EarthqVis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(EarthqVis)
library(ggplot2)
```
This package is designed to visualize earthquake data.


## eq_location_clean

**Description**
*eq_location_clean* Make Location name nicer

**Usage**
eq_location_clean(data)

**Arguments**
*data*: A dataset

**Value**
cleaned dataset

**Examples**
```{r, results='hide'}
readr::read_delim(raw_data,
                  delim = "\t") %>%
                      eq_location_clean() 
```

## eq_clean_data
**Description**
*eq_clean_data* Curate data

**Usage**
eq_clean_data(data)

**Arguments**
*data*: A dataset

**Value**
curated dataset

**Examples**
```{r, results='hide'}
readr::read_delim(raw_data,
                  delim = "\t") %>%
                      eq_location_clean() 
```

## eq_create_label
**Description**
*eq_create_label* make label for popup on the map

**Usage**
eq_create_label(data)

**Arguments**
*data*: A dataset

**Value**
a list of labels consisting of Location, Number of Deaths and Magnitude for each earthquake

**Examples**
```{r, results='hide'}
readr::read_delim(raw_data,
                  delim = "\t") %>%
       eq_location_clean()%>%
       dplyr::mutate(popup_text = eq_create_label(.)) 
```

## eq_map
**Description**
*eq_map* Show Points on map

**Usage**
eq_map(data, annot_col)

**Arguments**
*data*: A dataset

*annot_col*: selected column for showing in pop-up

**Value**
show earthquake points on maps

**References**
https://rstudio.github.io/leaflet/markers.html

**Examples**
```{r, fig.height = 3, fig.width = 7, fig.align = "center", warning=FALSE}
readr::read_delim(raw_data,
                  delim = "\t") %>%
       eq_clean_data() %>%
    dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
    dplyr::mutate(popup_text = eq_create_label(.)) %>% 
    eq_map(annot_col = "popup_text")
```

## geom_timeline
**Description**
*geom_timeline* make a timeline of earthquakes for countries

**Usage**
geom_timeline(
  mapping = NULL,
  data = NULL,
  stat = "identity",
  position = "identity",
  na.rm = FALSE,
  show.legend = T,
  inherit.aes = TRUE,
  ...
)

**Examples**
```{r, fig.height = 3, fig.width = 7, fig.align = "center" , warning=FALSE}
ex_data <- readr::read_delim(raw_data,
                  delim = "\t") %>%
                      eq_clean_data() %>%
                      filter(YEAR>2010) %>%
filter(COUNTRY %in% c("IRAN","CHINA"))
ggplot2::ggplot(data = ex_data, aes(x = ex_data$DATE ,
                          y = ex_data$COUNTRY,
                          size = ex_data$EQ_PRIMARY,
                          alpha = ex_data$DEATHS)) +
 geom_timeline()+
 theme_light()+
 labs(size = "Strength (Richter)",
      alpha = "Number of deaths")+
 xlab("Time") + ylab("")
```

## geom_timeline_label

**Description**
*geom_timeline_label* make labels for a timeline of earthquakes for countries

**Usage**
geom_timeline_label(
  mapping = NULL,
  data = NULL,
  stat = "identity",
  position = "identity",
  na.rm = FALSE,
  show.legend = F,
  inherit.aes = TRUE,
  ...
)

**Examples**
```{r, fig.height = 3, fig.width = 7, fig.align = "center", warning=FALSE}
ex_data <- readr::read_delim(raw_data,
                  delim = "\t") %>%
                      eq_clean_data() %>%
                      filter(YEAR>2010) %>%
filter(COUNTRY %in% c("IRAN","CHINA"))
ggplot2::ggplot(data = ex_data, aes(x = ex_data$DATE ,
                          y = ex_data$COUNTRY,
                          size = ex_data$EQ_PRIMARY,
                          alpha = ex_data$DEATHS,
                          label = ex_data$LOCATION_NAME)) +
 geom_timeline_label(n_max = 20)+
 geom_timeline()+
 theme_light()+
 labs(size = "Strength (Richter)",
      alpha = "Number of deaths")+
 xlab("Time") + ylab("")
```

## ggproto_timeline
**Description**
*ggproto_timeline* build ggproto object for geom_timeline

**Usage**
ggproto_timeline

**Format**
An object of class ggproto_timeline (inherits from Geom, ggproto, gg) of length 6.

## ggproto_timeline_label
**Description**
*ggproto_timeline_label* build ggproto object for geom_timeline_label

**Usage**
ggproto_timeline_label

**Format**
An object of class ggproto_timeline_label (inherits from Geom, ggproto, gg) of length 6.
